2H qSIP Calculations

### 2021-10-19 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

peaks_mapped <- peaks_mapped %>% 
  group_by(sample_id) %>% 
  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
         inc_time_d_str = paste(inc_time_d, "Days"),
         f_label = 0.005)

inc_time_zero <- peaks_mapped %>% 
  filter(inc_time_d == 0)

peaks_mapped <- peaks_mapped %>%
  group_by(sample_id) %>%
  mutate(f_start = case_when(
           inc_time_d == 0 ~ at2H,
           inc_time_d != 0 ~ inc_time_zero$at2H
           ),
         terrain = case_when(
           substr(sample_id, 1, 1) == "t" ~ "Niwot Ridge Tundra",
           substr(sample_id, 1 ,1) == "c" ~ "Gordon Gulch Conifer Forest",
           substr(sample_id, 1 ,1) == "m" ~ "Gordon Gulch Meadow",
           substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))

>>>>

peaks_mapped <- peaks_mapped %>% 
  group_by(sample_id) %>% 
  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
         inc_time_d_str = paste(inc_time_d, "Days"),
         f_label = 0.005,
         t_series_id = paste0(substr(sample_id, 1,1), 
                              substr(sample_id, 5,5)))

inc_time_zero <- peaks_mapped %>% 
  filter(inc_time_d == 0) %>% 
  select(sample_id, compound, at2H) %>% 
  mutate(f_start = at2H)
         # extract first and lass code of sample_id

```{r}
peaks_mapped <- peaks_mapped %>%
  group_by(sample_id) %>%
  mutate(f_start = case_when(
           inc_time_d == 0 ~ at2H,
           inc_time_d != 0 ~ inc_time_zero$at2H
           ),
         terrain = case_when(
           substr(sample_id, 1, 1) == "t" ~ "Niwot Ridge Tundra",
           substr(sample_id, 1 ,1) == "c" ~ "Gordon Gulch Conifer Forest",
           substr(sample_id, 1 ,1) == "m" ~ "Gordon Gulch Meadow",
           substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))
